Towards human SuperEEG

### 2018-10-08 paper/main.tex
finished draft of results

To gain insights into whether particular electrode locations might be
especially informative, we first computed the average reconstruction
accuracy across all of each patient's electrodes (using the
across-patients cross validation test; black histograms in
Fig.~\ref{fig:corrmap}A and C).  We labeled each patient's electrodes
in each dataset with the average reconstruction accuracy for that
patient.  In other words, we assigned every electrode from each
patient the same value, reflecting how well the activity patterns at
those electrodes were reconstructed on average.  Next, for each voxel
in the 4~mm$^3$ MNI brain, we computed the average value across any
electrode (from any patient) that came within 20 MNI units of that
voxel's center.  Effectively, we computed an \textit{information
  score} for each voxel, reflecting the average reconstruction
accuracy across any patients with electrodes near each voxel-- where
the averages were weighted to reflect patients who had more electrodes
implanted near that location. This yielded a single map for each
dataset, highlighting regions that are especially promising
implantation targets in terms of providing full-brain activity
information via SuperEEG (Fig.~\ref{fig:informap}A, B).  Despite task
and patient differences across the two datasets, we nonetheless found
that the maps of the most promising implantation targets derived from
both datasets were similar (voxelwise correlation between information
scores across the two datasets: $r = XXX, p = XXX$).  While the
correspondence between the two maps was not perfect, our finding that there were
some commonalities between the two maps lends support to the notion
that different brain areas are differently informative about
full-brain activity patterns.  Further, regions like XXX and XXX that
exhibited strong information scores in both datasets may be especially
promising implantation targets.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.} \textbf{A. \& B. } The glass
    brain maps displays the average reconstruction correlations (by patient, across
    all electrodes) for patients with electrodes within a 20 MNI unit diameter sphere centered on
    each location for dataset 1 and dataset 2. \textbf{C.} Correlation between z-transformed correlations by voxel for dataset 1 vs. dataset 2.}
  \label{fig:informap}
\end{figure}

@@

%why does it work?  redundancy of brain
A fundamental assumption of the SuperEEG algorithm is that the data
covariance matrix is stable over time and across people.  This is a
useful simplification.  However, a growing body of evidence from the
fMRI community suggests that the data covariance matrix changes in
meaningful ways over time (for example, the data covariance matrix
changes from moment-to-moment during story listening, serving as a
unique ``fingerprint'' for each moment of the story; further, these
task-driven timepoint-specific covariance fingerprints appear to be
largely preserved across people~\cite{SimoEtal16, MannEtal17}).  These
findings indicate that the full-brain covariance matrix is not stable
over time.  Other recent work has shown that people's resting state
connectivity matrices may be used to uniquely identify individuals and
predict fluid intelligence scores~\cite{FinnEtal15}.  This indicates
that the full-brain covariance matrix is not stable across people.  If
the fundamental stability assumptions that SuperEEG relies on are
violated, how can the SuperEEG algorithm still accurately recover LFP
data?  It is important to recognize that the fact that variability
(over time or across people) is predictive (e.g., of cognitive states
during story listening or fluid intelligence scores) does not
necessarily mean that this variability is large in magnitude.  Rather,
we have long known that brain structure is tightly preserved across
individuals (and over time, at least on the timescale of typical
clinical and experimental recording sessions), and any functional
changes must occur within the framework of the underlying structural
anatomy.  Nevertheless, one could imagine future improvements to the
SuperEEG approach that leverage resting state fMRI or structural data
[e.g., diffusion tensor imaging (DTI)] to estimate Bayesian priors over
the correlation matrices inferred, in the current framing, using only
ECoG data.  Further, relaxing the assumption that the covariance
matrix is stable (over time and/or across people), and/or
incorporating more detailed brain conductance models (e.g., informed
by structural MRI scans) may improve the predictive performance of the
approach.

@@

\bibliography{CDL-bibliography/memlab.bib}
\bibliographystyle{Science}

>>>>

To gain insights into whether particular electrode locations might be
especially informative, we first computed the average reconstruction
accuracy across all of each patient's electrodes (using the
across-patients cross validation test; black histograms in
Fig.~\ref{fig:corrmap}A and C).  We labeled each patient's electrodes
in each dataset with the average reconstruction accuracy for that
patient.  In other words, we assigned every electrode from each
patient the same value, reflecting how well the activity patterns at
those electrodes were reconstructed on average.  Next, for each voxel
in the 4~mm$^3$ MNI brain, we computed the average value across any
electrode (from any patient) that came within 20 MNI units of that
voxel's center.  Effectively, we computed an \textit{information
  score} for each voxel, reflecting the average reconstruction
accuracy across any patients with electrodes near each voxel-- where
the averages were weighted to reflect patients who had more electrodes
implanted near that location. This yielded a single map for each
dataset, highlighting regions that are especially promising
implantation targets in terms of providing full-brain activity
information via SuperEEG (Fig.~\ref{fig:informap}A, B).  Despite task
and patient differences across the two datasets, we nonetheless found
that the maps of the most promising implantation targets derived from
both datasets were similar (voxelwise correlation between information
scores across the two datasets: $r = XXX, p = XXX$).  While the
correspondence between the two maps was not perfect, our finding that
there were some commonalities between the two maps lends support to
the notion that different brain areas are differently informative
about full-brain activity patterns.  Further, regions like XXX, XXX,
and XXX that exhibited strong information scores in both datasets may
be especially promising implantation targets.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.}
    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
    reflect the weighted average reconstruction accuracy across all
    electrodes from any patients with at least one electrode within 20
    MNI units of the given voxel.  {B. Dataset 2 information score by
      voxel.}  This panel is in the same format as Panel A.
    \textbf{C. Correspondence in information scores by voxel across
      Datasets 1 and 2.}  Same format as Figure~\ref{fig:density}C.}
  \label{fig:informap}
\end{figure}

@@

@@

%why does it work?  redundancy of brain
A fundamental assumption of the SuperEEG algorithm is that the data
covariance matrix is stable over time and across people.  This is a
useful simplification.  However, a growing body of evidence from the
fMRI community suggests that the data covariance matrix changes in
meaningful ways over time (for example, the data covariance matrix
changes from moment-to-moment during story listening, serving as a
unique ``fingerprint'' for each moment of the story; further, these
task-driven timepoint-specific covariance fingerprints appear to be
largely preserved across people~\cite{SimoEtal16, MannEtal18}).  These
findings indicate that the full-brain covariance matrix is not stable
over time.  Other recent work has shown that people's resting state
connectivity matrices may be used to uniquely identify individuals and
predict fluid intelligence scores~\cite{FinnEtal15}.  This indicates
that the full-brain covariance matrix is not stable across people.  If
the fundamental stability assumptions that SuperEEG relies on are
violated, how can the SuperEEG algorithm still accurately recover LFP
data?  It is important to recognize that the fact that variability
(over time or across people) is predictive (e.g., of cognitive states
during story listening or fluid intelligence scores) does not
necessarily mean that this variability is large in magnitude.  Rather,
we have long known that brain structure is tightly preserved across
individuals (and over time, at least on the timescale of typical
clinical and experimental recording sessions), and any functional
changes must occur within the framework of the underlying structural
anatomy.  Nevertheless, one could imagine future improvements to the
SuperEEG approach that leverage resting state fMRI or structural data
[e.g., diffusion tensor imaging (DTI)] to estimate Bayesian priors over
the correlation matrices inferred, in the current framing, using only
ECoG data.  Further, relaxing the assumption that the covariance
matrix is stable (over time and/or across people), and/or
incorporating more detailed brain conductance models (e.g., informed
by structural MRI scans) may improve the predictive performance of the
approach.

@@

\bibliography{CDL-bibliography/memlab.bib}
\bibliographystyle{apa}
